Comparison of dimensionality reduction schemes for parallel global optimization algorithms \thanks{The study was supported by the Russian Science Foundation, project No 16-11- 10150}

### 2018-04-14 2018/RSD/MultiEvolvents/RSD.tex
RSD: update picture for non univalent evolvent

\begin{figure}[ht]
    \centering
    \subfloat[Two shifted evolvents on the hypercubes $D_0$ and $D_1$]{{\includegraphics[width=.5\textwidth]{pictures/shifted.pdf}}\label{fig:shifted_ev}}
    %\subfloat[Hypercubes $D_l$]{{\includegraphics[width=.4\textwidth]{pictures/shifted_cube.png}}\label{fig:shifted_cube}}
    \subfloat[Two rotated evolvents on the same plane]{{\includegraphics[width=.5\textwidth]{pictures/rotated.pdf}}\label{6_fig_9}}
    \caption{Multiple mappings}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \subfloat[Smooth
evolvent]{{\includegraphics[width=.6\textwidth]{pictures/smooth.pdf}}\label{fig:smooth}}
    \subfloat[Numerical non-univalent
evolvent]{{\includegraphics[width=.4\textwidth]{pictures/noninjective.pdf}}\label{fig:noninjective}}
    \caption{Different evolvents}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \subfloat[Two shifted evolvents on the hypercubes $D_0$ and $D_1$]{{\includegraphics[width=.5\textwidth]{pictures/shifted.pdf}}\label{fig:shifted_ev}}
    %\subfloat[Hypercubes $D_l$]{{\includegraphics[width=.4\textwidth]{pictures/shifted_cube.png}}\label{fig:shifted_cube}}
    \subfloat[Two rotated evolvents on the same plane]{{\includegraphics[width=.5\textwidth]{pictures/rotated.pdf}}\label{6_fig_9}}
    \caption{Multiple evolvents built with low density }
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \subfloat[Smooth evolvent]{{\includegraphics[width=.6\textwidth]{pictures/smooth.pdf}}\label{fig:smooth}}
    \subfloat[Non-univalent
evolvent]{{\includegraphics[width=.4\textwidth]{pictures/noninjective.pdf}}\label{fig:noninjective}}
    \caption{Different evolvents built with low density}
\end{figure}
